---
title: "Data Structures & Algorithms Notes"
author: "Joshua Goldberg"
date: "`r format(Sys.time(), '%B, %d %Y')`"
always_allow_html: yes
output:
  github_document: 
  pdf_document: default
editor_options: 
  chunk_output_type: inline
---

```{r Global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.asp=0.618, fig.path='Figs/',
                      warning=FALSE, message=FALSE, cache=TRUE)
```

```{r Preamble, echo=FALSE}
# Enter package in p_load()
# If package is not installed, p_load() will install and load the package
if(!"pacman" %in% rownames(installed.packages())) {
  install.packages("pacman")
  }
pacman::p_load(tidyverse, ggthemes, here)

# Set default ggplot theme to tufte
theme_set(ggthemes::theme_tufte())
```

```{r Copy-files, echo=FALSE, eval=FALSE}
# Enter files to load to project directory in from = "~/Downloads/your_file_name_here"
file.copy(from = "~/Downloads/", to = here::here(), 
          overwrite = TRUE, recursive = FALSE, 
          copy.mode = TRUE)
```

# How to solve problems

1. Don't Panic!

1. What are the inputs?

1. What are the outputs?

1. Work out some examples by hand.

1. Simple mechanical solution.

1. Develop incrementally in small steps and test as we go.

*Dont' optimize prematurely! Use simple and correct code.*

# Python lists are essentially dynamic arrays

"We will not get into all of the details, but the important thing you need to know for this course is the following: If you were to look under the hood, you would find that a Python list is essentially implemented like an array (specifically, it behaves like a dynamic array, if you're curious). In particular, the elements of a Python list are contiguous in memory, and they can be accessed using an index."






