---
title: "Runtime Analysis for Unscramble Computer Science Problems"
author: "Joshua Goldberg"
date: "`r format(Sys.time(), '%B, %d %Y')`"
always_allow_html: yes
output:
  github_document: 
  pdf_document: default
editor_options: 
  chunk_output_type: inline
---

```{r Global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.asp=0.618, fig.path='Figs/',
                      warning=FALSE, message=FALSE)
```

```{r Preamble, echo=FALSE}
# Enter package in p_load()
# If package is not installed, p_load() will install and load the package
if(!"pacman" %in% rownames(installed.packages())) {
  install.packages("pacman")
  }
pacman::p_load(tidyverse, ggthemes, here)

# Set default ggplot theme to tufte
theme_set(ggthemes::theme_tufte())
```

```{r Copy-files, echo=FALSE, eval=FALSE}
# Enter files to load to project directory in from = "~/Downloads/your_file_name_here"
file.copy(from = "~/Downloads/", to = here::here(), 
          overwrite = TRUE, recursive = FALSE, 
          copy.mode = TRUE)
```

The below runtime analyses are Worst Case Big-O approximations.

## Reading data

Reading data is required for all the below tasks, so we will address it first.

```{r}

```

Notation: $O(n^2)$

- $O(n^2)$: Reading two files are based on inputs ([complexity-of-f-in-python](https://stackoverflow.com/questions/51801213/complexity-of-f-seek-in-python).

## Task 0

What is the first record of texts and what is the last record of calls?

```{python eval=FALSE}
print(f"First record of texts, {texts[0][0]} texts {texts[0][1]} at time "
      f"{texts[0][2]}.")

total_calls = len(calls) - 1

print(f"Last record of calls, {calls[total_calls][0]} called {calls[total_calls][1]} "
      f"at {calls[total_calls][2]}, lasting {calls[total_calls][3]} seconds.")
```

Notation: $O(1)$

The operations are not dependent on iteration.

## Task 1

How many different telephone numbers are there in the records? 

```{python eval=FALSE}
numbers = set()

for text, call in zip(texts, calls):
    for i in range(0, 2):
        numbers.add(text[i])
        numbers.add(call[i])

print(f"There are {len(numbers)} different telephone numbers in the records.")
```

Notation: $O(n+logn)$

- $O(n+logn)$: Two explicit `for` loops. One is logarithmic.

## Task 2

Which telephone number spent the longest time on the phone during the period? Don't forget that time spent answering a call is also time spent on the phone.

```{python eval=FALSE}
dials = {call[0]: int(call[3]) for call in calls}
receives = {call[1]: int(call[3]) for call in calls}
receives_ex_dials = dict()

for (k, v), (k2, v2) in zip(dials.items(), receives.items()):
    if k in receives.keys():
        dials[k] = v + receives[k]
    if k2 not in dials.keys():
        receives_ex_dials[k2] = v2

dials.update(receives_ex_dials)

max_phone = max(dials, key=lambda key: dials[key])

print(f"{max_phone} spent the longest time, {dials[max_phone]} seconds, on the "
      f"phone during September 2016.")
```

Notation: $O(n^6)$

- $O(n^2)$: `Two set()` comprehensions

- $O(n)$: One explicit `for` loop (should iterating over `zip()` also be included? See task 4, which shows is $O(n)$.)

-  $O(n^2)$: Two `in` operations inside the `for` loop

- $O(n)$: `max()` ([how-efficient-is-pythons-max-function](https://stackoverflow.com/questions/5454030/how-efficient-is-pythons-max-function))

- Note that dictionary `update()` method is expected to be $O(1)$ ([time-complexity-of-python-dictionary-get-update-always-o1](https://stackoverflow.com/questions/52504598/time-complexity-of-python-dictionary-get-update-always-o1))

## Task 3

The area code for fixed line telephones in Bangalore is "(080)".
Fixed line numbers include parentheses, so Bangalore numbers
have the form (080)xxxxxxx.)

Part A: Find all of the area codes and mobile prefixes called by people
in Bangalore.
 - Fixed lines start with an area code enclosed in brackets. The area
   codes vary in length but always begin with 0.
 - Mobile numbers have no parentheses, but have a space in the middle
   of the number to help readability. The prefix of a mobile number
   is its first four digits, and they always start with 7, 8 or 9.
 - Telemarketers' numbers have no parentheses or space, but they start
   with the area code 140.

Part B: What percentage of calls from fixed lines in Bangalore are made
to fixed lines also in Bangalore? In other words, of all the calls made
from a number starting with "(080)", what percentage of these calls
were made to a number also starting with "(080)"?

```{python eval=FALSE}
bangalore_calls = [call for call in calls if call[0].startswith("(080)")]

bangalore_dialed = [call[1] for call in bangalore_calls]

called_areas = []

for call in bangalore_dialed:
    if re.search("\(\w+\)", call):
        called_areas.append(re.search(r'(\(.*?\))', call).group(1))
    elif re.search(r'(^[7|8|9])', call):
        called_areas.append(call[0:4])
    clean_calls = sorted(list(set(called_areas)))
    print("The numbers called by people in Bangalore have codes:")
    for call in clean_calls:
        print(call)

total_calls = len(bangalore_calls)

bangalore_to_bangalore = len([call for call in bangalore_calls if call[
    1].startswith("(080)")])

percentage = round(bangalore_to_bangalore / total_calls, 4) * 100

print(f"{percentage} percent of calls from fixed lines in Bangalore are calls to other fixed lines in Bangalore.")

```

Notation: $O(n + nlogn)$

- $O(n)$: One explicit `for` loop

- Regex is typically $O(n)$ ([what-is-the-complexity-of-regular-expression](https://stackoverflow.com/questions/4378455/what-is-the-complexity-of-regular-expression)), but we are checking with an `if` statement, so no sequencing is needed.

- `sorted()` introduces $O(nlogn)$, according to python [documentation](https://wiki.python.org/moin/TimeComplexity).

## Task 4

The telephone company wants to identify numbers that might be doing telephone marketing. Create a set of possible telemarketers: these are numbers that make outgoing calls but never send texts, receive texts or receive incoming calls.

```{python eval=FALSE}
dials = {call[0] for call in calls}
receives = [call[1] for call in calls]
real_people = set()

for text, receive in zip(texts, receives):
    for i in range(0, 2):
        real_people.add(text[i])
    real_people.add(receive)

potential_telemarketers = {call for call in dials if call not in real_people}
potential_telemarketers = sorted(list(potential_telemarketers))

print(f"These numbers could be telemarketers: {potential_telemarketers}")
print(f"Total potential telemarketers: {len(potential_telemarketers)}")
```

Notation: $n^6+nlogn+logn$

- $O(n^2)$: Two `set()` comprehension

- $O(n)$: One `list()` comprehension

- $O(n)$: One `in` operation inside `list()` comprehension

- $O(n+logn)$: Two explicit `for` loops. One is logarithmic.

- $O(nlogn)$: `sorted()`

- $O(n)$: Iterating on `zip()` object ([what-is-the-time-complexity-of-zip-in-python](https://stackoverflow.com/questions/36877715/what-is-the-time-complexity-of-zip-in-python))
